Formalizing the Kolmogorov extension Theorem in Lean

### 2023-09-14 Manuscript/proof_outline.tex
rename compactfamily to compactsystem

\begin{minted}[highlightlines={1}, mathescape, numbersep=5pt, framesep=5mm, bgcolor=mygray]{Lean}
  def IsCompactFamily (p : Set α → Prop) : Prop :=
    ∀ C : ℕ → Set α, (∀ i, p (C i)) → ⋂ i, C i = ∅ →
    ∃ (s : Finset ℕ), ⋂ i ∈ s, C i = ∅
\end{minted}

@@

%%     theorem isCompactFamily_cylinders :
%% IsCompactFamily (fun t ↦ t ∈ closedCompactCylinders α)

%% lemma AddContent.sigma_additive_of_regular [Nonempty α] (hR : SetRing R) (m : AddContent R)
%%     (hm_ne_top : ∀ {s} (_ : s ∈ R), m s ≠ ∞)
%%     (hC : IsCompactFamily C) (hCR : C ⊆ R)
%%     (h_reg : ∀ A (_ : A ∈ R) (ε : ℝ≥0∞) (_ : 0 < ε), ∃ K ∈ C, K ⊆ A ∧ m (A \ K) ≤ ε)
%%     ⦃f : ℕ → Set α⦄ (hf : ∀ i, f i ∈ R) (hUf : (⋃ i, f i) ∈ R) (h_disj : Pairwise (Disjoint on f)) :
%%     m (⋃ i, f i) = ∑' i, m (f i)

>>>>

\begin{minted}[highlightlines={1}, mathescape, numbersep=5pt, framesep=5mm, bgcolor=mygray]{Lean}
  def IsCompactSystem (p : Set α → Prop) : Prop :=
    ∀ C : ℕ → Set α, (∀ i, p (C i)) → ⋂ i, C i = ∅ →
    ∃ (s : Finset ℕ), ⋂ i ∈ s, C i = ∅
\end{minted}

@@

%%     theorem isCompactSystem_cylinders :
%% IsCompactSystem (fun t ↦ t ∈ closedCompactCylinders α)

%% lemma AddContent.sigma_additive_of_regular [Nonempty α] (hR : SetRing R) (m : AddContent R)
%%     (hm_ne_top : ∀ {s} (_ : s ∈ R), m s ≠ ∞)
%%     (hC : IsCompactSystem C) (hCR : C ⊆ R)
%%     (h_reg : ∀ A (_ : A ∈ R) (ε : ℝ≥0∞) (_ : 0 < ε), ∃ K ∈ C, K ⊆ A ∧ m (A \ K) ≤ ε)
%%     ⦃f : ℕ → Set α⦄ (hf : ∀ i, f i ∈ R) (hUf : (⋃ i, f i) ∈ R) (h_disj : Pairwise (Disjoint on f)) :
%%     m (⋃ i, f i) = ∑' i, m (f i)
